Rhyme: A Query Language for Nested Data Structures

### 2024-12-16 paper.tex
minor update

We also compared the execution time of \rhyme and TACO, we run the generated code on 4 randomly generated sparse vectors with 10 percent sparsity. The result is shown in Figure \ref{evaluationpic}. As we can observe, \rhyme 's generated code can achieve roughly $80\%$ performance of TACO in the example query. The performance gap could be caused by the fact that TACO generates native C code for the computation kernel while our header file is purely written in C++ and heavily utilize STL containers. Our backend also adds several abstractions over both the sparse tensor data structure and the co-iteration method which could add additional overhead. But it should be noted that \rhyme is still an ongoing project and we could develop a pure C backend and generate more specialized C code with not much development effort. Also, compared with TACO, \rhyme manage to integrate relational algebra with sparse tensor algebra in a unified framework and perform several loop optimization likes loop hoisting and fusion.

@@

We also compared the execution time of \rhyme and TACO by running the generated code on four randomly generated sparse vectors with 10$\%$ sparsity. The results are shown in Figure \ref{evaluationpic}. As observed, \rhyme's generated code achieves approximately $80\%$ of TACO's performance for the example query.\par

>>>>

We also compared the execution time of \rhyme and TACO, we run the generated code on 4 randomly generated sparse vectors with 10 percent sparsity. The result is shown in Figure \ref{evaluationpic}. As we can observe, \rhyme 's generated code can achieve roughly $86\%$ performance of TACO in the example query. The performance gap could be caused by the fact that TACO generates native C code for the computation kernel while our header file is purely written in C++ and heavily utilize STL containers. Our backend also adds several abstractions over both the sparse tensor data structure and the co-iteration method which could add additional overhead. But it should be noted that \rhyme is still an ongoing project and we could develop a pure C backend and generate more specialized C code with not much development effort. Also, compared with TACO, \rhyme manage to integrate relational algebra with sparse tensor algebra in a unified framework and perform several loop optimization likes loop hoisting and fusion.

@@

We also compared the execution time of \rhyme and TACO by running the generated code on four randomly generated sparse vectors with 10$\%$ sparsity. The results are shown in Figure \ref{evaluationpic}. As observed, \rhyme's generated code achieves approximately $86\%$ of TACO's performance for the example query.\par
